---
title: "Untitled"
author: "James Vesto"
date: "10/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(magick)
library(cowplot)
library(modelr)
library(lubridate)
library(grid)
```
Step #1 import data

```{r, message=FALSE}
methanolysis_data <- read_csv("/Users/jamesvesto/R-Studio Files/Projects/terpene-kinetics/data/JIV-01-08zg2d.csv")
#note make sure to confirm the path each time!
methanolysis_data
```

Step #2 determine concentration of ISTD in NMR sample

Note: the internal standard used was 1-Bromo-4-chlorobenzene, the procedure was consistently to add the mg amount (reported in data file) to 1 mL of MeOD, then to add .1 mL of the ISTD solution to 5 mL of MeOD w/ carene nitrate. The MW of the ISTD is 191.45 g/mol. 

```{r}
ISTD_MW <- 191.45 #(g/mol)
dilution_factor <- .1/.6# volume of ISTD added over total volume of sample (no units: mL/mL)

methanolysis_data_conc <- methanolysis_data %>% mutate(
  ISTD_conc = ISTD_mg_mL/ISTD_MW*dilution_factor*1000)%>% #(mmol/L) Note: mg/mL=g/L, the 1000 is to convert M into mM
  select(-ISTD_mg_mL) #removing no longer necessary column

remove(dilution_factor, ISTD_MW, methanolysis_data) #cleaning environment

methanolysis_data_conc
```
Step #3: Correcting integration by ISTD 

```{r}
methanolysis <- methanolysis_data_conc %>% 
  mutate(integral_mM= integral*ISTD_conc/ISTD)%>%
  select(-ISTD,-ISTD_conc,-integral)%>%
  group_by(assignment)

remove(methanolysis_data_conc)
```


Step 1: make a simple ggplot coordinate system

```{r}
img <- image_read("/Users/jamesvesto/R-Studio Files/Projects/terpene-kinetics/images/NMR_assignments.png")

image <- image_fill(img, 'none')
raster <- as.raster(image)
```

Trying the method listed in R for Data Science on pages 377-379

```{r}
methanolysis_product <- methanolysis %>%
  mutate(ln_conc = log(integral_mM),inverse_conc =1/integral_mM)%>%
  rename(zero = integral_mM, first = ln_conc, second = inverse_conc)%>%
  gather(zero , first, second , key="order", value="integral_mM")

methanolysis_product$order = factor(methanolysis_product$order, levels = c("zero","first","second"), labels= c("Zeroth Order (mM)", "First Order (ln(mM))", "Second Order (1/mM)"))
methanolysis_product$assignment = factor(methanolysis_product$assignment, levels = c("SM_A","SM_B"), labels = c("Proton Assignment A", "Proton Assignment B"))

ggplot(filter(methanolysis_product, assignment!="product"), aes(time_s, integral_mM))+
  geom_line()+ 
  facet_grid(cols = vars(assignment), rows=vars(order), scales = "free_y", as.table=TRUE)+
  theme_bw()+
  labs(x="Time (s)", y="Concentration")

```
These graphs show that the reaction is first order!! WOOO!

```{r}
methanolysis2 <- methanolysis%>%
  mutate(log_conc=log(integral_mM))

SM_A_model <- lm(log_conc~time_s, data=subset(methanolysis2, assignment=="SM_A"))
grid_A <- subset(methanolysis2, assignment=="SM_A")%>%
  data_grid(time_s) %>%
  add_predictions(SM_A_model, "log_conc")%>%
  mutate(integral_mM=exp(log_conc))

SM_B_model <- lm(log_conc~time_s, data=subset(methanolysis2, assignment=="SM_B"))
grid_B <- subset(methanolysis2, assignment=="SM_B")%>%
  data_grid(time_s) %>%
  add_predictions(SM_B_model, "log_conc")%>%
  mutate(integral_mM=exp(log_conc))

A_slope <- SM_A_model$coefficients[2]
A_intercept <- SM_A_model$coefficients[1]
B_slope <- SM_B_model$coefficients[2]
B_intercept <- SM_B_model$coefficients[1]

summary(SM_B_model)
slope <- rbind(A_slope, B_slope)
intercept <- rbind(A_intercept, B_intercept)
data.frame(slope, intercept)
```

```{r}
mplt <- ggplot(methanolysis, aes(time_s,integral_mM,color=assignment))+
  geom_point(size=1)+ 
  labs(x="Time (s)", 
       y="Concentration (mM)", 
       title="Trial #3 (test run) Carene Nitrate Methanolysis: JIV-01-08zg2d")+
  theme_bw()+ 
 # annotate("text", x=1400,y=.6, label=expression('[A]'[t]*'=[A]'[0]*'e'^{'-6.4E-4'*t}))+
  scale_color_manual(values=c("#FFC107", "#004D40", "#1E88E5"), 
                       name="Proton Assignment",
                       breaks=c("product", "SM_A", "SM_B"),
                       labels=c(expression(H[C]), expression(H[A]), expression(H[B])))+
  theme(legend.position = "none")+
  annotation_raster(raster,7500, 11000,16, 30)+
  geom_line(data=grid_A,color="#004D40")+
  geom_line(data=grid_B,color="#1E88E5")
```


```{r}
save_plot("/Users/jamesvesto/R-Studio Files/Projects/terpene-kinetics/images/plots/JIV-01-08zg2d.jpg", mplt)
rm(list=ls()) 
```

